Toxic code snippets on Stack Overflow

### 2017-10-29 cloverflow-tse/cloverflow.tex
Fixed a small typo.

	\item \textbf{An online code
		clone oracle:} The 2,302 manually investigated and validated online clone pairs
	are available for download\footnote{\FIXME{ADD THIS URL}} and
	can be used as a clone oracle. \end{enumerate}

@@

\begin{table}
	\centering
	\caption{Number of online clones reported by Simian and SourcererCC}
	\label{tab:orig_stats}
	%\small
	%\resizebox{\columnwidth}{!}{%
	\begin{tabular}{lrr}
		\toprule
		Stats & \multicolumn{1}{c}{Total clone pairs} & \multicolumn{1}{c}{Average clone size} \\
		\midrule
		Simian & 721 & 16.61 \\
		SourcererCC & 1,678 & 17.86 \\
		\bottomrule
	\end{tabular} %
	%}
\end{table}

>>>>

	\item \textbf{An online code
		clone oracle:} The 2,302 manually investigated and validated online clone pairs
	are available for download\footnote{https://ucl-crest.github.io/cloverflow-web} and
	can be used as a clone oracle. \end{enumerate}

@@

\begin{table}
	\centering
	\caption{Number of online clones reported by Simian and SourcererCC}
	\label{tab:orig_stats}
	%\small
	%\resizebox{\columnwidth}{!}{%
	\begin{tabular}{lrr}
		\toprule
		Tool & \multicolumn{1}{c}{Total clone pairs} & \multicolumn{1}{c}{Average clone size} \\
		\midrule
		Simian & 721 & 16.61 \\
		SourcererCC & 1,678 & 17.86 \\
		\bottomrule
	\end{tabular} %
	%}
\end{table}
